---
title: "A Simulation Study"
author: "Didier Termont"
output: 
  html_document:
    theme: readable
    highlight: tango
    toc: true
    toc_float: true
    df_print: paged
---

```{r setup , include=FALSE }
knitr::opts_chunk$set(echo = TRUE, comment=NA )
klippy::klippy(lang=c("r","markdown"),position=c("top","right"))
```
# 1 Data {.tabset .tabset-pills}

## Normal distribution

We first recall the definition of a normal random variable (displayed through a quote environment).

> A random variable $X$ is said to be normally distributed with mean $\mu$ and variance $\sigma^2$ if it has a probability density function $f:R→R^+$ given by
> $f(x) = \frac{1}{\sqrt(2\pi)\sigma}exp\{-\frac{(x-\mu)^2}{2\sigma^2}\}$ (1.1)

This is written as $X \sim N(\mu,\sigma^2)$.

More details about normal random variables (r.v.) can be found on [this page](https://en.wikipedia.org/wiki/Normal_distribution).

## Simulations

The R function `rnorm` allows us to draw simulations from the normal density function as given by Equation (1.1).

Let fix some parameters and generate some data.

```{r simu, class.source='klippy'}
set.seed(1)
n <- 100
mu <- 100
stdev <- 2
v <- stdev^2
b0 <- 2
b1 <- 1
X <- rnorm(n, mu, stdev)
Y <- b0 + b1 * X + rnorm(n)
samp <- data.frame(X = X, Y = Y)
samp
```

As you can see, we draw **100** realizations from two random variables : $X \sim N(100, 4)$ and $Y=b_0+b_1×X+\epsilon$, with $b_0= 2$, $b_1= 1$, and $\epsilon \sim  N(0,1)$.

Observe that if you re- render the Rmd (source) file with different parameters `(n, mu, stdev, b0, b1)`, then all the numbers above get updated automatically. Check it!

The simulated data will be use to fit a linear model, See the section [Linear model](https://elghouch.github.io/LSTAT2030/Labs/Lab1/2E.html#ll).

# 2 Descriptive statistics {.tabset .tabset-pills}

## Summary statistics

* The empirical mean and variance of $X$ are **100** and **3**, respectively.
* The empirical mean and variance of $Y$ are **102** and **4**, respectively.

Let’s summarize the simulations with the help of the summary function.

```{r, echo=FALSE, comment=NA}
summary(samp,digits=3)
```

## Histogram of X

We can use the `hist` function to display, for example, the histogram of $X$:

```{r}
hist(samp$X)
```

## Histogram of Y

Similarly here is a histogram of $Y$:
```{r}
hist(samp$Y)
```

# 3 Linear model {.tabset .tabset-pills}

## The model

We built a linear regression model using
```{r}
fit <- lm(Y~X,data=samp)
```

We get the following output
```{r}
summary(fit)$coef
```

The coefficient of determination ($R^2$) of the model is **0.778**

## Scatter plot with regression line

```{r}
plot(Y~X,data=samp)
abline(fit)
```

## Residuals and fitted values

The model fitted values (fitted) and residuals (fit$residuals) are

## Diagnostic plot