---
title: "An RMarkdown report"
author: "Termont Didier"
output: 
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(scipen=1,digits=3)
```

# Data description

In this project we consider the classical iris data set that can be found in the base R package datasets. iris has **`r ncol(iris)`** columns named **`r colnames(iris)`** and **`r nrow(iris)`**
observations.

To get help about columns, run `?iris`.

The data set `iris` is
```{r}
iris
```

# Descriptive analysis
First, we compute some descriptive statistics with the `summary()` function:

```{r}
summary(iris) |> kableExtra::kbl(caption = "Descriptive statistics") |> kableExtra::kable_styling()
```
Second, we use the function `aggregate` to get the following table that shows the means of the 4 numerical variables for each species.
```{r}
aggregate(. ~ Species, data = iris, mean) |> kableExtra::kbl(caption="Mean by species") |> kableExtra::kable_styling()
```

# Linear regression
We use the function `cor()` to get the Pearson’s coefficients of correlation between all our numeric variables:
```{r}
cor(iris[1:4]) |> kableExtra::kbl(caption="Pearson's coefficients of correlation") |> kableExtra::kable_styling()
```
Here are 3 scatter plots that show the association between `Petal.Length` and the other numerical variables.
```{r,fig.asp=0.9,out.width="50%"}
plot(Sepal.Length~Petal.Length,data=iris)
plot(Sepal.Width~Petal.Length,data=iris)
plot(Petal.Width~Petal.Length,data=iris)
```

Now, we would like to explain the variations in the length of the sepal as a function of the length of the petal. To do so, we use the following linear regression `lm(Sepal.Length ~ Petal.Length, data = iris)`. Here is the summary of this model:
```{r}
model <- lm(Sepal.Length~Petal.Length,data=iris)
summary(model)$coef |> kableExtra::kbl(caption = "Summary of lm: Sepal.Length ~ Petal.Length") |> kableExtra::kable_styling()
```
The model equation is $$\widehat{Sepal.length} = a + b Petal.Length$$
Here are the data with the regression line:
```{r}
plot(Sepal.Length~Petal.Length,data=iris,xlab="Petal length",ylab="Sepal length")
abline(model)
```

Finally, we use the ´plot(reg)´ command to get some graphical representations of the residuals.
